A Standardized Effect Size for Evaluating and Comparing the Strength of Phylogenetic Signal

### 2020-07-17 Manuscript/PNAS-Adams-01.tex

For \(\lambda\), deriving an effect size is more challenging, as
\(\lambda\) does not have a sampling distribution from which the
standard error and confidence intervals may be obtained. Confidence
intervals are therefore generated for the values of \(\lambda\) that
intersect the log-likehihood profile for corresponding percentiles of
the \(\chi^2\) distribution used to compare the putative model to a null
model with \(\lambda = 0\) {[}\textbf{add ref: MLC thinks Boettiger
paper?}{]}. Thus, an effect size for \(\lambda\) may be found as:

>>>>

For \(\lambda\), deriving an effect size is more challenging, as
\(\lambda\) does not have a sampling distribution from which the
standard error and confidence intervals may be obtained, and estimates
from the Hessian matrix from PGLS are unreliable (23). Confidence
intervals are therefore generated for the values of \(\lambda\) that
intersect the log-likehihood profile for corresponding percentiles of
the \(\chi^2\) distribution used to compare the putative model to a null
model with \(\lambda = 0\) {[}\textbf{add ref: MLC thinks Boettiger
paper?}{]}. Thus, an effect size for \(\lambda\) may be found as:
